Robust Spectroscopic Inference with Imperfect Models

### 2014-11-03 tex/paper.tex
just kidding: now its the last time!

We can now compute the covariance matrix employed in the likelihood calculation 
(Eq.~\ref{eqn:lnlikelihood}) as the linear combination of the trivial pixel-by-pixel noise matrix, 
an interpolation error kernel ($\mathcal{K}^{\rm int}$; see the Appendix), and the global and local 
kernels discussed above, 
\begin{equation}
\vC_{ij}(\cov)  = b \, \delta_{ij} \, \sigma_i + \mathcal{K}_{ij}^{\rm int} + w_{ij} \, \Kglobal_{ij}(\vp_{{\mathsf C}, g}) + 
                  \Klocal_{ij}(\vp_{{\mathsf C}, l}), 
\end{equation}
with (hyper-)parameters $\cov = [\vp_{{\mathsf C}, g}, \vp_{{\mathsf C}, l}]$.  The factor $b$ is 
a parameter that scales up the Poisson noise in each pixel by a constant factor to account for 
additional detector or data reduction uncertainties (e.g., read noise, uncertainties in the 
spectral extraction procedure, etc.); typically $b < 1.1$ for well-calibrated optical spectra.  If 
there are $N_{\rm loc}$ local covariance patches (see Section \ref{subsec:MCMC} on how this is 
determined), then there are $4N_{\rm loc}+2$ elements in the set of covariance (hyper-)parameters, 
$\cov$.

>>>>

We can now compute the covariance matrix employed in the likelihood calculation 
(Eq.~\ref{eqn:lnlikelihood}) as the linear combination of the trivial pixel-by-pixel noise matrix 
and the global and local kernels discussed above,\footnote{See the Appendix for a modification of 
the likelihood function that incorporates interpolation uncertainty.} 
\begin{equation}
\vC_{ij}(\cov)  = b \, \delta_{ij} \, \sigma_i + w_{ij} \, \Kglobal_{ij}(\vp_{{\mathsf C}, g}) + 
                  \Klocal_{ij}(\vp_{{\mathsf C}, l}), 
\end{equation}
with (hyper-)parameters $\cov = [\vp_{{\mathsf C}, g}, \vp_{{\mathsf C}, l}]$.  The factor $b$ is 
a parameter that scales up the Poisson noise in each pixel by a constant factor to account for 
additional detector or data reduction uncertainties (e.g., read noise, uncertainties in the 
spectral extraction procedure, etc.); typically $b < 1.1$ for well-calibrated optical spectra.  If 
there are $N_{\rm loc}$ local covariance patches (see Section \ref{subsec:MCMC} on how this is 
determined), then there are $4N_{\rm loc}+2$ elements in the set of covariance (hyper-)parameters, 
$\cov$.
